% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template

\documentclass[sigconf, nonacm, table]{acmart}
\usepackage{xcolor} 
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subcaption}
\usepackage{bm}
\usepackage{wrapfig}
\usepackage{makecell}
\usepackage[subtle]{savetrees}
\usepackage{enumitem} 
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{diagbox}
\usepackage{balance}

%% The following content must be adapted for the final version
% paper-specific
\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{17} 
\newcommand\vldbissue{1}
\newcommand\vldbyear{2023}
% should be fine as it is
\newcommand\vldbauthors{\authors} 
\newcommand\vldbtitle{\shorttitle} 
% leave empty if no availability url should be set
\newcommand\vldbavailabilityurl{github.com/cirquit/hivemind-multi-cloud}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{plain} 
\definecolor{diff1}{RGB}{21,87,255}

\begin{document}
\title[]{How Can We Train Deep Learning Models Across \\Clouds and Continents? An Experimental Study}
%%
%% The "author" command and its associated commands are used to define the authors and their affiliations.
\author{Alexander Isenko}
\affiliation{%
  \institution{Technical University of Munich}
  \city{Munich}
  \country{Germany}
}
\email{alex.isenko@tum.de}
 
\author{Ruben Mayer}
\affiliation{%
  \institution{University of Bayreuth}
  \city{Bayreuth}
  \country{Germany}
}
\email{ruben.mayer@uni-bayreuth.de}

\author{Hans-Arno Jacobsen}
\affiliation{%
  \institution{University of Toronto}
  \city{Toronto}
  \country{Canada}
}
\email{jacobsen@eecg.toronto.edu}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\input{content/abstract}
\maketitle
\vspace*{-2mm}
%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\pagestyle{\vldbpagestyle}
\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
\vldbauthors. \vldbtitle. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
\endgroup
\vspace*{-2mm}
\begingroup
\renewcommand\thefootnote{}\footnote{\noindent
This work is licensed under the Creative Commons BY-NC-ND 4.0 International License. Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license. For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}. Copyright is held by the owner/author(s). Publication rights licensed to the VLDB Endowment. \\
\raggedright Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
ISSN 2150-8097. \\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
}\addtocounter{footnote}{-1}\endgroup
%%% VLDB block end %%%

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\ifdefempty{\vldbavailabilityurl}{}{
\vspace{.3cm}
\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
The source code, data, and/or other artifacts have been made available at \url{\vldbavailabilityurl}.
\endgroup
}
%%% VLDB block end %%%
\vspace*{-1mm}
\section{Introduction}
\label{sec:introduction}
\begin{tikzpicture}
\begin{scope}[overlay]
\node[text width=17.5cm] at ([yshift=-7cm,xshift=-1cm]current page.south) {(c) Owner 2023. This is the authors' version of the work. It is posted here for your personal use. Not for redistribution. \newline The definitive version is currently in submission.};
\end{scope}
\end{tikzpicture} 
\input{content/introduction}

\section{Deep Learning On Spot Instances}
\label{sec:distributed-dl}
\input{content/distributed-dl}

\section{Model Suitability For Distributed Training} 
\label{sec:model-suitability}
\input{content/model-suitability}

%\vspace*{-3mm}
\section{Geo-distributed Performance}
\label{sec:geodistributed-performance} 
\input{content/geodistributed-performance}

\section{Multi-cloud Performance}
\label{sec:multicloud-performance}
\input{content/multicloud-performance}
 
\section{Hybrid-cloud Performance}
\label{sec:hybrid-cloud-performance}
\input{content/hybrid-cloud-performance}

\vspace*{-2mm}
\section{Further Insights}
\label{sec:further-insights}
\input{content/further-insights}

\vspace*{-3mm}
\section{Lessons Learned}
\label{sec:lessons-learned}
\input{content/lessons-learned}

\vspace*{-4mm}
\section{Related Work}
\label{sec:related-work}
\input{content/related-work}

\section{Conclusion}
\label{sec:conclusion}
\input{content/conclusion}

%\begin{acks}
%This work was supported by the [...] Research Fund of [...] (Number [...]). Additional funding was provided by [...] and [...]. We also thank [...] for contributing [...].
%\end{acks}

%\clearpage

\bibliographystyle{ACM-Reference-Format}
\bibliography{main}

\end{document}
\endinput
